What Can Stack Traces Tell us about of the use Exceptions in Java?

### 2014-07-11 android-stacks.tex
ckecked and unckeded debate improvements
including examples of strange wrappings.

Although exception handling mechanism has been embedded in several programming languages 
as show above,   the exception handling code is often generally poorly understood and the least
tested part of software systems.

There is a long-lasting debate about the pros and cons of checked and unchecked exceptions 
~\cite{javatut,stackoverlow,debate},\footnote{152 questions in Stackoverlow
are related to this debate}. The debates, however, are based on the developers own experience in
using both models. There is a lack of empirical study tackling the pros and cons of each model.

@@

>>>>

@@

\subsubsection{Checked Exception wrapping Error}

We could observe that in 4 projects this strange wrapping happend 7 times in total.

\subsubsection{Error wrapping Checked Exception}

We could observe that in 7 projects this strange wrapping happend 8 times in total.
Inspecting the stack traces we could observe that 7 out of 8 wrappings were caused
by the reflection java library on which "java.lang.OutOfMemoryError"
"java.lang.NoSuchMethodError" were wrapped into a "java.lang.reflect.InvocationTargetException".

In one of the cases, however, in project OpenDocument.droid a java.lang.Exception was 
wrappings a java.lang.OutOfMemoryError.
This general handlers is a known bad practice and here we could observe a bad consequence of
such bad practice.

\begin{table}
\centering
\begin{tabular}{llll}
    \hline
    \bfseries{Project} & \bfseries{Stars} & \bfseries{Watchers} & \bfseries{Forks} \\
    \hline
androidremocons &  9  &  2    & 10 \\
android-timepicker &  73  &  13    & 32 \\
PathfinderOpenReference &  23  &  12   & 15 \\
ActionBarSherlock &  5926  &   767  & 3356 \\
OpenDocument.droid &  40  &  9   & 12 \\
TouchDB-Android &  -  &  -    & - \\
ContractionTimer &  -  &  -    & - \\
\hline
  \end{tabular}
\caption{Projects containing wrappings (Error-Checked)}
\label{tab:wrappings2}
\end{table}

\subsubsection{Runtime Exception wrapping Error}

\subsubsection{Error wrapping Runtime Exception}

\subsubsection{Runtime wrapping Checked Exception}

\subsubsection{Checked wrapping Runtime Exception}
